---
title: "Final"
author: "YY"
date: "5/2/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,include=FALSE, message=FALSE, warning=FALSE}
library(PoEdata); library(xtable); library(knitr); library("lmtest"); library(zoo);library(carData);library("sandwich");library(ggplot2);library(gridExtra);library(lmtest);library(readxl);library(car);library(stargazer);library(lattice);library(survival);library(Formula);library(nortest);library(foreign);library(nnet);library(reshape2);library(png);library(scales);library(dplyr);library(tidyr);library(latticeExtra); library(cowplot); library(lubridate);library(imputeTS); library(forecast);library(kableExtra); library(xtable); library(knitr); library("tidyr");library(tidyverse);library(broom);library(AER); library(systemfit);library(Formula);library(nortest);library(foreign);library(nnet);library(kableExtra);library(xtable);library(mfx); library(sampleSelection); library(prediction); library(ivregEX);library(censReg); library(truncreg); library(mfx);library(multcomp);library("RcmdrMisc");library(mlogit); library(dynlm);library(orcutt); library(nlWaldTest);library(pdfetch); library(TTR); library(tseries);library(kableExtra); library(truncreg);library(nlWaldTest); library(PoEdata); library(sampleSelection);  library(forecast); library(TTR); library(tseries); library(plm);library(skimr);library(pivottabler);library(pivottabler);library(lessR)
```

```{r,message=FALSE, warning=FALSE}
#input two datasets
online_retail_Year1011 <- read_excel("C:/Users/yueyu/Dropbox/PC/Desktop/BD620/Project/online_retail_II/online_retail_Year1011.xlsx")
online_retail_Year0910 <- read_excel("C:/Users/yueyu/Dropbox/PC/Desktop/BD620/Project/online_retail_II/online_retail_Year0910.xlsx")
```

```{r,message=FALSE, warning=FALSE}
#check the header
names(online_retail_Year0910)
names(online_retail_Year1011)
```

```{r,message=FALSE, warning=FALSE}
#combine two datasets
online_retail<-rbind(online_retail_Year0910, online_retail_Year1011)
```

```{r,message=FALSE, warning=FALSE}
summary(online_retail)
```

```{r}
colnames(online_retail) <- c("Invoice","StockCode", "Description", "Quantity", "InvoiceDate", "Price", "CustomerID", "Country")
```

```{r,message=FALSE, warning=FALSE}
#Find duplicated data and remove
N_online_retail<-distinct(online_retail)
dim(N_online_retail)
```

```{r,message=FALSE, warning=FALSE}
#This step is to omit the missing customer ID data. Using this dataset to do the further analysis.
online_retail_1 <-filter(N_online_retail,!is.na(N_online_retail$CustomerID))
```

```{r,message=FALSE, warning=FALSE}
#omit negative quantity data.
online_retail_2 <-subset(online_retail_1,Quantity >=0)
summary(online_retail_2)
```

```{r}
online_retail_2$Sales <- online_retail_2$Quantity*online_retail_2$Price
head(online_retail_2)
```

```{r}
#Creat a country, United Kingdom as 1, other country as 0, because most of transaction in United kingdom
online_retail_2$UK <- ifelse(online_retail_2$Country == 'United Kingdom',1,0)
head(online_retail_2)
```

```{r}
online_retail_2$Date <- as_date(as.POSIXct(online_retail_2$InvoiceDate))
head(online_retail_2)
```

#Customer segmentation, creat Recency, frequency and monitery.

```{r,message=FALSE, warning=FALSE}
RFM <- online_retail_2 %>%
group_by(CustomerID) %>%
summarise(Recency=as.numeric(as.Date('2012-01-01')-max(Date)),
Frequency= n_distinct(Invoice), Monetary= sum(Sales))
summary(RFM)
```

```{r}
head(RFM)
```
Simple clustering
```{r}
Rank_R<-mutate(RFM, Recency_rank = ntile(RFM$Recency,4))
head(Rank_R)
Rank_R$Recncy_N <- 5-Rank_R$Recency_rank
Rank_R <- subset(Rank_R,select=-c(Recency_rank))
head(Rank_R)
Rank_F <- mutate(Rank_R, Frequency_Score = ntile(Rank_R$Frequency,4))
head(Rank_F)
Rank_M <- mutate(Rank_F, Monetary_Score = ntile(Rank_F$Frequency,4))
head(Rank_M)
```

```{r}
Rank_M$Score <- Rank_M$Recncy_N+Rank_M$Frequency_Score+Rank_M$Monetary_Score
head(Rank_M)
```


After grouping the customer score, I want to cluster the customer as three type. Gold, Silver, Bronze.
```{r}
Rank_M$segment <- ifelse(Rank_M$Score>9, "A", ifelse(Rank_M$Score>6 & Rank_M$Score<=9, "B", ifelse(Rank_M$Score>3 & Rank_M$Score<=6,"C","D")))
head(Rank_M)
```

```{r}
Rank_seg <- Rank_M %>% 
  group_by(segment) %>% 
  summarise(Recency_m = mean(Recency),
            Frequency_m = mean(Frequency),
            Monetary_m = mean(Monetary))
Rank_seg
```
```{r}
table(Rank_M$segment)
```

K-mean clustering
choosing K
```{r}
RFM_scale <- scale(RFM[,2:4])
head(RFM_scale)
```

After normalization, we need to decide value for ‘k’ to decide how many clustering our data will be. 
```{r}
wss <- function(RFM_scale, maxCluster = 9) {
    SSw <- (nrow(RFM_scale) - 1) * sum(apply(RFM_scale, 2, var))
    SSw <- vector()
    set.seed(111)
    for (i in 2:maxCluster) {
        SSw[i] <- sum(kmeans(RFM_scale, centers = i)$withinss)
    }
    plot(1:maxCluster, SSw, type = "o", xlab = "Number of Clusters", ylab = "Within groups sum of squares", pch=19)
}
wss(RFM_scale)
```
This plot draw a curve is means that between “within the sum of squares” (WSS) and the number of clusters.So, according to these results, after the 4 cluster, because after the 4, the value of sum of squares are change slowly.

Then chose the cluster as 4 to do further analysis.

partition the data



```{r}
set.seed(111)
rans <- sample(1:nrow(RFM), 0.6 * nrow(RFM)) 
# Training set
RFM_train <- RFM[rans,] 
# Validation set
RFM_valid <- RFM[-rans,]
```

```{r}
RFM_k_mean_train <- kmeans(RFM_train,4)
```

```{r}
RFM_train$cluster <- as.factor(RFM_k_mean_train$cluster)
RFM_train
```

```{r}
RFM_train_mean <- RFM_train %>% 
  group_by(cluster) %>% 
  summarise(Recency = mean(Recency),
            Frequency = mean(Frequency),
            Monetary = mean(Monetary))
RFM_train_mean
```

```{r}
RFM_k_mean_valid <- kmeans(RFM_valid,4)
```

```{r}
RFM_valid$cluster <- as.factor(RFM_k_mean_valid$cluster)
RFM_valid
```

```{r}
RFM_valid_mean <- RFM_valid %>% 
  group_by(cluster) %>% 
  summarise(Recency = mean(Recency),
            Frequency = mean(Frequency),
            Monetary = mean(Monetary))
RFM_valid_mean
```



```{r}

```



```{r}
set.seed(111)
RFM_k_mean <- kmeans(RFM_scale,4)
```

```{r}
K_mean <- RFM
head(K_mean)
```

```{r}
K_mean$cluster <- as.factor(RFM_k_mean$cluster)
K_mean
```

```{r}
RFM_means <- K_mean %>% 
  group_by(cluster) %>% 
  summarise(Recency = mean(Recency),
            Frequency = mean(Frequency),
            Monetary = mean(Monetary))
RFM_means
```

```{r}
table(K_mean$cluster)
```

